Modeling electrostatics in molecular biology: A tutorial of DelPhi and associated resources [Article v\versionnumber]

### 2019-08-27 article-manuscript/article-manuscript-tutorial-v01.tex
Update article-manuscript-tutorial-v01.tex

\begin{equation}
I_B = \frac{e_c^2}{(4\pi\epsilon_0\epsilon_{ext}k_BT)} 
\end{equation}
\begin{equation}
\kappa^{-1} = \sqrt{\left(\frac{\epsilon_0\epsilon_{ext}k_BT}{2 \times 10^3N_Ae_c^2} \right)}
\end{equation}
\begin{equation}
\Delta G_{nz}([salt], R) = \frac{1}{2}k_B T \left(\frac{Q}{e_c}\right)^2\frac{I_B \kappa^{-1}}{R(R+\kappa^{-1})}
\end{equation}
\begin{equation}
\Delta G_z(R) = \frac{1}{2}k_B T \left(\frac{Q}{e_c}\right)^2\frac{I_B}{R}
\end{equation}
\begin{equation}\label{eqn:saltation_23}
\Delta\Delta G_{nz}([salt]) = \Delta G_{nz}([salt], R) - \Delta G_z(R)
\end{equation}

where $I_B$ is Bjerrum length, $ c $ is ionic strength in M, $ k_B $ is Boltzman constant, $ T $ is absolute temperature, $ e_c $ is the electronic charge, $ \kappa^{-1} $ is Debye length, $ \epsilon_0 $ is the electric permittivity of free space, $ \epsilon_{ext} $ is the external dielectric constant of the medium, $ R $ is the radius of charged sphere, $ \Delta G_{nz}([salt], R) $ is electrical energy of charged sphere in solvent with salt, $ \Delta G_z(R) $ is the electrical energy of charged sphere in solvent without salt, $ \Delta\Delta G_{nz}([salt]) $ is the saltation energy of charged sphere.

>>>>

\begin{equation}
I_B = \frac{e_c^2}{(4\pi\epsilon_0\epsilon_{ext}k_BT)} 
\end{equation}
\begin{equation}
\kappa^{-1} = \sqrt{\left(\frac{\epsilon_0\epsilon_{ext}k_BT}{2 \times 10^3N_Ae_c^2 I} \right)}
\end{equation}
\begin{equation}
\Delta G_{nz}([salt], R) = \frac{1}{2}k_B T \left(\frac{Q}{e_c}\right)^2\frac{I_B \kappa^{-1}}{R(R+\kappa^{-1})}
\end{equation}
\begin{equation}
\Delta G_z(R) = \frac{1}{2}k_B T \left(\frac{Q}{e_c}\right)^2\frac{I_B}{R}
\end{equation}
\begin{equation}\label{eqn:saltation_23}
\Delta\Delta G_{nz}([salt]) = \Delta G_{nz}([salt], R) - \Delta G_z(R)
\end{equation}

where $I_B$ is Bjerrum length, $ c $ is ionic strength in M, $ k_B $ is Boltzman constant, $ T $ is absolute temperature, $ e_c $ is the electronic charge, $ I $ is the ionic strength (or salt concentration) in molar unit i.e. mol/L, $ \kappa^{-1} $ is Debye length, $ \epsilon_0 $ is the electric permittivity of free space, $ \epsilon_{ext} $ is the external dielectric constant of the medium, $ R $ is the radius of charged sphere, $ \Delta G_{nz}([salt], R) $ is electrical energy of charged sphere in solvent with salt, $ \Delta G_z(R) $ is the electrical energy of charged sphere in solvent without salt, $ \Delta\Delta G_{nz}([salt]) $ is the saltation energy of charged sphere.
